---
title: "Example Web API recommender creation"
author: Anton Antonov
date: 2021-02-23
output: html_notebook
---

```{r setup}
library(plumber)
library(SparseMatrixRecommender)
library(SMRMon)
library(magrittr)
library(Matrix)
```

```{r get-data}
savedObjectsDirName <- "../objects/"
modelID <- "B0KR-2021-02-23T12-33-57"

load( file = file.path( savedObjectsDirName, paste0( modelID, "-", "dfDiceJobsProcessed.RData" ) ) )
load( file = file.path( savedObjectsDirName, paste0( modelID, "-", "lsTaxonomyTagsRecommenders.RData" ) ) )
load( file = file.path( savedObjectsDirName, paste0( modelID, "-", "lsTaxonomyTagsLSANoTextObjects.RData" ) ) )

smrObj <- smrDiceJobs
dfSMRData <- dfDiceJobsProcessed
```


# Introduction

In order to demonstrate the creation and use Web API and a proxy recommender for it:

1. In a separate R-session run this file

2. Run the examples in the file ["PRSMon-retrieval-experiments.Rmd"](https://github.com/antononcube/R-packages/blob/master/PRSMon-R/notebooks/PRSMon-retrieval-experiments.Rmd)

# Recommender examples

Here is an example using the recommender object:

```{r}
smrObj %>%  
  SMRMonRecommendByProfile( profile = c("Skill:java", "Skill:agile", "Skill:finance"), nrecs = 12, normalizeQ = TRUE ) %>% 
  SMRMonJoinAcross( data = dfSMRData ) %>% 
  SMRMonTakeValue
```


Show recommender's tag types:

```{r}
smrObj %>% SMRMonTakeTagTypes
```


# Make plumber calls

Build up the [plumber](https://www.rplumber.io) (Web API) object:

```{r}
plObj <- 
  plumber::pr() %>% 
  plumber::pr_get( path = "/recommend", 
                   handler = function( history, nrecs = 12, extendQ = FALSE ) { 
                     
                     history <- trimws( strsplit(history, split = ",")[[1]] )
                     
                     extendQ <- as.logical(extendQ)
                     
                     nrecs <- as.numeric(nrecs)
                     
                     if(extendQ) { 
                       smrObj %>% 
                         SMRMonRecommend( history = history, nrecs = nrecs ) %>%
                         SMRMonJoinAcross( data = dfSMRData ) %>% 
                         SMRMonTakeValue
                     } else {
                       smrObj %>% 
                         SMRMonRecommend( history = history, nrecs = nrecs ) %>%
                         SMRMonTakeValue
                     }
                     
                   }, 
                   serializer = plumber::serializer_json() ) %>% 
  
    plumber::pr_get( path = "/recommendbyprofile", 
                   handler = function( profile, nrecs = 12, extendQ = FALSE ) { 
                     
                     profile <- trimws( strsplit(profile, split = ",")[[1]] )
                     
                     extendQ <- as.logical(extendQ)
                     
                     nrecs <- as.numeric(nrecs)
                    
                     if( extendQ ) {
                       smrObj %>% 
                         SMRMonRecommendByProfile( profile = profile, nrecs = nrecs ) %>%
                         SMRMonJoinAcross( data = dfSMRData ) %>% 
                         SMRMonTakeValue
                     } else {
                       smrObj %>% 
                         SMRMonRecommendByProfile( profile = profile, nrecs = nrecs ) %>%
                         SMRMonTakeValue
                     }
                     
                   }, 
                   serializer = plumber::serializer_json() ) %>% 
  
      plumber::pr_get( path = "/classifybyprofile", 
                   handler = function( tagtype, profile ) { 
                     
                     profile <- trimws( strsplit(profile, split = ",")[[1]] )
                     
                     smrObj %>% 
                       SMRMonClassifyByProfile( tagType = tagtype, profile = profile) %>%
                       SMRMonTakeValue
                     
                   }, 
                   serializer = plumber::serializer_json() )
```

Start the server of the `plumber` object:

```{r}
plumber::pr_run( pr = plObj )
```

